\documentclass{resume} % Use the custom resume.cls style
\usepackage{pifont}
  \usepackage[utf8]{inputenc}
  % select font
  \usepackage{mathptmx}
  \usepackage[T1]{fontenc}
  \usepackage[default]{lato}
  \usepackage[inline]{enumitem} 
  \usepackage{fontawesome}
  \usepackage{xcolor}

  
% \setlist[itemize]{topsep=-\noskip}
% \renewcommand{\familydefault}{Arvo}
\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{XUAN TRUONG NGUYEN} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{\faPhone{ (+84) 901798750 } \faEnvelope{ truongnx.9499@gmail.com} }
\address{\faGithub{\href{https://www.github.com/xtruog94}{  Github }} \faLinkedin{ \href{https://www.linkedin.com/in/truongnx9499/}{ LinkedIn }} \faExternalLink{\href{https://www.truongnx.com}{ Portfolio}}}  %

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{OBJECTIVE}

{As a Bachelor of Mathematics and Informatics graduated with honors, having over 2 years of experience in NLP Engineering, I want to challenge myself in a larger and more specialized environment.}


\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Bachelor of Mathematics and Informatics}\\
\textit{ Hanoi University of Science and Technology} \hfill {\textit{Aug. 2017 - Jan. 2022}}

Graduate with Honor Degree - CPA : 3.2

{\bf Master of Mathematics and Informatics}\\
\textit{Hanoi University of Science and Technology} \hfill {\textit{April 2022 - Now}}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{EXPERIENCE}

\textbf{Vietnam Compare Joint Stock Company} \hfill \textit{July 2020 - June 2021}\\
\textit{NLP Engineer}
% \vspace{0.5em}
 \begin{itemize}
     \item Explored and extracted information from a huge amount of products on multiple e-commerce platforms.
     \item Analyzed user's behaviors to improve company products in product recommendation, product classification.
 \end{itemize}

 \textbf{Vietnam Compare Joint Stock Company} \hfill \textit{June 2021 - Now}\\
\textit{Machine Leaning Team Leader}

 \begin{itemize}
     \item Develop state-of-the-art Natural Language Processing models.
     \item Lead a team of NLP engineers in developing and implementing algorithms for natural language processing.
     \item Collaborate with product managers and system departure to ensure the effectiveness of NLP solutions.
 \end{itemize}

\textbf{Dantri Electronic News} \hfill \textit{June 2021 - Now}\\
\textit{Machine Leaning Team Leader}

 \begin{itemize}
     \item Manage NLP projects from conception to completion, ensure that progress and quality of projects.
     \item Communicate with cross-functional teams and stakeholders to understand business requirements and provide technical solutions.
     \item Develope and implemente text classification, sentiment analysis, and topic modeling algorithms which can be used in near-realtime for millions users.
    \item Train and mentor junior NLP engineers.
 \end{itemize}
 

\end{rSection} 

%----------------------------------------------------------------------------------------
%	PROJECT SECTION
%----------------------------------------------------------------------------------------
\pagebreak

\begin{rSection}{PROJECTS}
    \textbf{User-based Recommendation System} \hfill {\textit{Oct. 2022 - Dec. 2022}}
    \begin{itemize}
        \item Collected and analyzed users behaviors based on a huge amount of data.
        \item Developed a near-real time personalized recommendation news system for over 1000 users per second.
        \item Utilized state-of-the-art model in NLP engineering and other tools such as Neo4j, Redis and Elasticsearch to develop the new system.
        \item Improved considerably users interaction.
    \end{itemize}
    
     
    \textbf{Recommend related products system}
     \begin{itemize}
     \setlength\itemsep{-0.5 em}
        \item Defined project goals and created a roadmap to ensure progress and effectiveness of the project.
        \item Led a team in developing a recommendation system which can suggest related products. 
         \item Collaborated with the product team to evaluate model efficiency and make data-driven decisions to improve customer experience.
     \end{itemize}

\textbf{Chatbot for an Japanese e-commerce website}
     \begin{itemize}
     \setlength\itemsep{-0.5 em}
        \item Developed an end-to-end chatbot to handle customer queries and promoting products.
        \item Created a roadmap and managed work progress of the project.
        \item Conducted experiments using ChatGPT to improve the quality of the system.
        \item Collaborated with the software development team to integrate the chatbot into the company's website and mobile app.
     \end{itemize}
     
     
\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
        Programming Languages: & Python, Js\\
        Libraries and toolkits: & Numpy, Pytorch, Django, FastAPI, Transformers\\
        Data technologies: & Redis, Elasticsearch, Kafka, RabbitMQ, Neo4j
    \end{tabular}
    
\end{rSection}
\vspace{0.5em}
\begin{rSection}{ACHIEVEMENTS}
    \textbf{BKAI-NAVER Challenge 2022 - Vietnamese Intent Detection and Slot Tagging.} \hfill {\textit{April 2022 - May 2022}}
    \begin{itemize}
        \item Hosted by BKAI Center, SOICT of Hanoi University of Science and Technology and NAVER with purpose is resolved real problems in Vietnam. 
        \item Developed a detection system which can detect the user's intent and classify entities in requirement of user.
        \item The proposed model achieved best accuracy rate with 75\%.
    \end{itemize}
    \textbf{Zalo AI Challenge 2022 - End-to-End Question Answering.} \hfill {\textit{Nov. 2022 - Sep 2022}}
    \begin{itemize}
        \item An annual contest organized by Zalo with the desire to use AI to resolve concerned problems in Vietnam.
        \item Utilized state-of-the-art model and tactics to solve problems.
        \item Enhanced team management skills as well as problem solving abilities. 
    \end{itemize}
\end{rSection}

\end{document}
